Datasheet for 'Nudge Data Repository dataset

### 2024-12-04 other/datasheet/datasheet_template.qmd
Update "datasheet_template.qmd" and "datasheet_template.pdf"
fixed some typos, and changed the subtitle

---
title: "Datasheet for 'Nudge Data Repository dataset'"
subtitle: "A Randomized Study to Evaluate the Effect of a Nudge via Weekly Emails on Students’ Attitudes Toward Statistics"
author: 
  - Shuangyuan Yang
thanks: "Code and data are available at: [https://github.com/Sophiaaa-Y/student-effort-analysis](https://github.com/Sophiaaa-Y/student-effort-analysis.git)."
date: today
date-format: long
abstract: "This datasheet provides a detailed description of a dataset compiled to evaluate the effect of weekly email nudges on attitudes towards statistics. The dataset includes over 1,000 records refined from a larger pool of student responses, especially focus on participants who experienced email nudges or different instructional formats. It includes variables such as demographic information, academic performance metrics, changes in attitudes such as affect, cognitive competence, interest, and difficulty, and behavioral engagement, each selected for their relevance to understanding predictors of educational outcomes."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- Yes. Each instance includes labels capturing the target variable, "change in effort," representing variations in student engagement. Supplementary labels include changes in affect, cognitive competence, difficulty, and interest, reflecting shifts in attitudes and behaviors post-intervention.

@@

2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- The dataset is associated with research conducted by the University of Toronto’s Department of Statistical Sciences. Relevant analyses, code, and findings are documented in the GitHub repository: [Nudge Data Repository](https://github.com/ntaback/nudgedata).

@@

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The dataset will be maintained by the research team at the University of Toronto’s Department of Statistical Sciences. They are responsible for ensuring its continued availability and quality.

2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- The dataset can be accessed and inquiries directed through the project‘s GitHub repository at [Nudge Data Repository](https://github.com/ntaback/nudgedata). Contact information for the research team is also provided within the repository.

>>>>

---
title: "Datasheet for 'Nudge Data Repository dataset'"
subtitle: "A Randomized Research to evaluate the Impacts of Weekly Email Nudges on Students' Attitudes Toward Statistics"
author: 
  - Shuangyuan Yang
thanks: "Code and data are available at: [https://github.com/Sophiaaa-Y/student-effort-analysis](https://github.com/Sophiaaa-Y/student-effort-analysis.git)."
date: today
date-format: long
abstract: "This datasheet provides a detailed description of a dataset compiled to evaluate the effect of weekly email nudges on attitudes towards statistics. The dataset includes over 1,000 records refined from a larger pool of student responses, especially focus on participants who experienced email nudges or different instructional formats. It includes variables such as demographic information, academic performance metrics, changes in attitudes such as affect, cognitive competence, interest, and difficulty, and behavioral engagement, each selected for their relevance to understanding predictors of educational outcomes."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- Yes. Each instance includes labels capturing the target variable, "change in effort", representing variations in student engagement. Supplementary labels include changes in affect, cognitive competence, difficulty, and interest, reflecting shifts in attitudes and behaviors post-intervention.

@@

2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- The dataset is associated with research conducted by the Department of Statistical Sciences at the University of Toronto. Relevant analyses, code, and findings are documented in the GitHub repository: [Nudge Data Repository](https://github.com/ntaback/nudgedata).

@@

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The research team at the University of Toronto's Department of Statistical Sciences will maintain the dataset. They are responsible for ensuring its continued availability and quality.

2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- The dataset can be accessed and inquiries directed through the project's GitHub repository at [Nudge Data Repository](https://github.com/ntaback/nudgedata). Contact information for the research team is also provided within the repository.
